COVID-19 Cases and Deaths in Canada in 2022 By Region, Age, and Sex

### 2024-12-14 paper/paper.qmd
Updated formatting
Removed typos

The data that was collected through hopistals and government institutions was gathered by COVerAGE-DB, a database that focuses on COVID related data. COVerAGE-DB consolidates this information into the dataset that was used in the analysis. COVerAGE-DB often gathers data relating to COVID such as the number of cases, deaths, tests, and vaccinations through governmental institutes such as health ministries and statistical offices. This data is then organized by other variables such as sex, region, country, and age and presented to the general public.

@@

For the analysis, a logistic regression model was chosen to predict the probability of a region or individual being classified as "high risk" based on key predictors such as age, sex, region, and the number of COVID-19 tests conducted. Logistic regression is particularly well-suited for this dataset because the outcome variable, high risk, is binary (e.g., classified as high risk or not). This makes logistic regression the most appropriate modeling technique as it directly estimates the probability of the binary outcome through the log-odds transformation. Compared to other models like linear regression, logistic regression avoids the issue of nonsensical predictions, such as probabilities below 0 or above 1, ensuring the interpretability of the results. Most importantly, logistic regression can handle both categorical and continuous predictors effectively. For this particular dataset, the key predictor variables are all categorical, even age is categorized by intervals. Therefore, it was extremely necessary for the model to be able to handl categorical data, which the logistic regression model is capable of.

@@

The systematic sampling method ensures that a sufficient sample size will be gathered and allows rather accurate prediction of the number of datapoints within the sample. It also ensures for uniform coverage and that sampling wouldn't be biased towards certain communities or subgroups. However, limitations could surface if the selected samples are not responding, not available, or refuse to co-operate. The systematic sampling method makes it hard to change the sample size if sitations like this were to occur.

@@

If a small number of households refuse to participate after repeated visits, the broad demographic information (such as region) can be recorded and later adjusted for during the data anlysis process. However, if a large number of households refuse to participate, specific parts of the data may need to be re-sampled or dropped, which may cause biases in the analysis. An attempt to address this may be to adjust the dataset based on known demographic information, but certain biases may be unavoidable.

@@

## Appendix E: Model Validation Details {#sec-appendixc}

@@

### Confusion Matrix

>>>>

The data that was collected through hospitals and government institutions was gathered by COVerAGE-DB, a database that focuses on COVID related data. COVerAGE-DB consolidates this information into the dataset that was used in the analysis. COVerAGE-DB often gathers data relating to COVID such as the number of cases, deaths, tests, and vaccinations through governmental institutes such as health ministries and statistical offices. This data is then organized by other variables such as sex, region, country, and age and presented to the general public.

@@

For the analysis, a logistic regression model was chosen to predict the probability of a region or individual being classified as "high risk" based on key predictors such as age, sex, region, and the number of COVID-19 tests conducted. Logistic regression is particularly well-suited for this dataset because the outcome variable, high risk, is binary (e.g., classified as high risk or not). This makes logistic regression the most appropriate modeling technique as it directly estimates the probability of the binary outcome through the log-odds transformation. Compared to other models like linear regression, logistic regression avoids the issue of nonsensical predictions, such as probabilities below 0 or above 1, ensuring the interpretability of the results. Most importantly, logistic regression can handle both categorical and continuous predictors effectively. For this particular dataset, the key predictor variables are all categorical, even age is categorized by intervals. Therefore, it was extremely necessary for the model to be able to handle categorical data, which the logistic regression model is capable of.

@@

The systematic sampling method ensures that a sufficient sample size will be gathered and allows rather accurate prediction of the number of datapoints within the sample. It also ensures for uniform coverage and that sampling wouldn't be biased towards certain communities or subgroups. However, limitations could surface if the selected samples are not responding, not available, or refuse to co-operate. The systematic sampling method makes it hard to change the sample size if situations like this were to occur.

@@

If a small number of households refuse to participate after repeated visits, the broad demographic information (such as region) can be recorded and later adjusted for during the data analysis process. However, if a large number of households refuse to participate, specific parts of the data may need to be re-sampled or dropped, which may cause biases in the analysis. An attempt to address this may be to adjust the dataset based on known demographic information, but certain biases may be unavoidable.

@@

```
\newpage
## Appendix E: Model Validation Details {#sec-appendixc}

@@

\newpage
### Confusion Matrix
